Geometric variational problems

### 2020-11-16 NSF2020/Description/preliminarywork.tex
RJR fixed frequ encies

\begin{wrapfigure}[22]{r}{0.5\textwidth}
\vspace{-5pt}
  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
  \vspace{-25pt}
  \caption{\label{fig:tank_treading} \footnotesize
    Panel A: A two-dimensional, 
    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s and
    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. (Compare with \cite{Brandner2019}).
    Panel B: Angular velocities for the outer and the inner leaflets.
    Panel C: The trajectory of the particle
    centers forms two ellipses with well-defined inclination angle
    $\Theta$. Panel D: The evolution of the inclination angle.
    Panels B and D share the same time axis.}
\end{wrapfigure}
We have simulated two-dimensional vesicles in shear flow
$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate
$\dot{\gamma}$,
%(The symbol shear rate is unrelated to interfacial tension.)
and the particle-based system mimics the behavior observed in continuous
vesicles~\cite{torres-sanchez_millan_arroyo_2019,
mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. The basic
pattern is that of a vesicle bilayer approaching a steady, tank-treading
ellipse (Figure~\ref{fig:tank_treading}C). We analyzed the simulation
data in the context of theoretical work on
tank-treading~\cite{Finken2008, PhysRevLett.106.158103}.
Jeffrey's equation predicts a tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
Figure~\ref{fig:tank_treading}B). In the particle simulation, we measured
a tank-treading frequency as the mean of the particle angular
velocities. The measured steady-state freque ncies were within 7\% of the predicted 
frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
The inclincation angle of the particle-based simulation also
follows the inclination angle $\Theta$ predicted by Jeffrey's
equation (Figure~\ref{fig:tank_treading}D), albeit with higher frequency oscillation
coming from particle reorganization.

>>>>

\begin{wrapfigure}[22]{r}{0.5\textwidth}
\vspace{-5pt}
  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
  \vspace{-25pt}
  \caption{\label{fig:tank_treading} \footnotesize
    Panel A: A two-dimensional, 
    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s and
    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. (Compare with \cite{Brandner2019}).
    Panel B: Angular velocities for the outer and the inner leaflets.
    Panel C: The trajectory of the particle
    centers forms two ellipses with well-defined inclination angle
    $\Theta$. Panel D: The evolution of the inclination angle.
    Panels B and D share the same time axis.}
\end{wrapfigure}
We have simulated two-dimensional vesicles in shear flow
$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate
$\dot{\gamma}$,
%(The symbol shear rate is unrelated to interfacial tension.)
and the particle-based system mimics the behavior observed in continuous
vesicles~\cite{torres-sanchez_millan_arroyo_2019,
mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. The basic
pattern is that of a vesicle bilayer approaching a steady, tank-treading
ellipse (Figure~\ref{fig:tank_treading}C). We analyzed the simulation
data in the context of theoretical work on
tank-treading~\cite{Finken2008, PhysRevLett.106.158103}.
Jeffrey's equation predicts a tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
Figure~\ref{fig:tank_treading}B). In the particle simulation, we measured
a tank-treading frequency as the mean of the particle angular
velocities. The measured steady-state frequencies were within 7\% of the predicted 
frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
The inclincation angle of the particle-based simulation also
follows the inclination angle $\Theta(t)$ predicted by Jeffrey's
equation (Figure~\ref{fig:tank_treading}D), albeit with higher frequency oscillation
coming from particle reorganization.
